Nirdizati: A Web-Based Tool for\\ Predictive Process Monitoring

### 2017-06-19 BPM17-demo-paper/paper.tex
change video URL
wording

Several approaches have been proposed to tackle with predictive process monitoring tasks.
However, so far, the predictive monitoring approaches have largely remained in the academic domain and
have not been widely applied in real-time scenarios, in which users require a continuous predictive support.

@@

A video demo of Nirdizati can be found at \url{https://youtu.be/hdfXMQTd4Qw}. A public release of Nirdizati Training and Nirdizati Runtime are available at \url{http://training.nirdizati.com} and \url{http://dashboard.nirdizati.com} respectively. The source code is available under the Lesser GNU Public License (LGPL) at \url{http://github.com/nirdizati}. 
\bibliographystyle{splncs03}
\bibliography{paper}

>>>>

Several approaches have been proposed in the literature to tackle common predictive process monitoring tasks.
However, so far, these approaches have largely remained in the academic domain and
have not been widely applied in real-time scenarios, in which users require a continuous predictive support.

@@

A video demo of Nirdizati can be found at \url{http://youtu.be/0nr14lX04-I}. A public release of Nirdizati Training and Nirdizati Runtime are available at \url{http://training.nirdizati.com} and \url{http://dashboard.nirdizati.com} respectively. The source code is available under the Lesser GNU Public License (LGPL) at \url{http://github.com/nirdizati}. 
\bibliographystyle{splncs03}
\bibliography{paper}
